\Huge Handwritten digit recognition

### 2017-02-08 doc/Paper.tex
Explain 2D-array choice in Implementation section

The trade-off is now clear: a lower batch size leads to greater accuracy while a greater batch size causes faster training.

@@

\paragraph{Predictive model} The core of the project is implemented in C++. This includes the neural network training and prediction. Data is maintained in memory using vectors from the standard library.

>>>>

The trade-off is now clear: a lower batch size leads to greater accuracy while a greater batch size causes faster training.
\\

Another

@@

\paragraph{Predictive model} The core of the project is implemented in C++. This includes the neural network training and prediction. Model weights and image samples are kept in memory using 2D-arrays.

Matrices build as vector of vectors (using the standard library implementation), while providing greater flexibility, cannot be sent efficiently using MPI. MPI deals with contiguous blocks of memory, while STL vectors are, by definition, dynamic. A workaround this is to send a matrix row-by-row. Our initial implementation used this method but unfortunately it provides little to no increase in parallelization performance and caused a general-rewrite.
